Title here

### 2017-01-04 portfolio/text/ms.Rmd
Finish discussion

<!--
Worldwide, fisheries confront the challenge of sustainable management (). While
many fisheries are well managed and productive, many are also rebuilding from
periods of over-exploitation (Worm et al. Science 2009). A common tactic to aid
in fisheries rebuilding is to modify regulations to reduce the unintended
harvest rebuilding stocks while allowing the continued harvest of healthy stocks
(need REF). Such bycatch reduction is an important goal for both ecological
(Crowder and Murawski 1998, Lewison et al. 2004) and economic (Curtis and Hicks
2000; Chakravorty and Nemoto 2001) reasons. Cumulatively, though, regulatory
changes for bycatch reduction as well as other reasons gradually lead to
fisheries that target one or a few species and individual fishers wishing to
participate in multiple fisheries must own (or purchase) multiple permits. Thus
a general consequence of fisheries regulations that are shown to improve
sustainability of fish stocks and avoid overfishing - including improved
assessments (Hilborn and Ovando 2014) and individual quota systems (Costello et
al. 2008 ) - may ultimately restrict individual diversification or at least make
developing a diverse fishing portfolio more expensive. Add Alaska example of
IFQs...?
-->

<!-- Conclusions + recommendations

- bring it out to wider than fisheries (farming, timber industry, ...)
- 2 dimensions to think about (revenue and variability); and the trade-off is
  fishery specific: effects within a permit strategy are permit specific;
  sometimes make more money by specializing... some highly variable single
  species permits make a ton of money
- broadly, diversification can provide a powerful form of protection from
  multiple sources of risk to income for those that rely on extracting natural
  resources, but not all forms of diversification are equal, and on an
  individual level there can be economic benefits to specializing and risks to
  adjusting ones strategy
- with increasing environmental variability and extremes due to climate change
  those that rely on natural resources for their livelihoods need approaches to
  buffer risk more than ever
- regulations that limit the ability to diversify can have other considerable
  benefits but it's important to be aware of trade-offs inherent in these
  regulations when making management decisions
-->

<!--Our results provide additional support for the idea that individual fishers can
reduce their income variability by diversifying their catch portfolios. However,
most individuals do not change their catch diversity substantially from year to
year [OLE: is there a supplemental figure or statistic that speaks to this
point?], and most strategies adopted by Alaskan fishermen lie in a high-risk,
high-reward quadrant in which reducing diversification increases both revenue
variability and expected revenue. Previous work has suggested that changes to
fisheries management such as limited entry or catch share programs may
inadvertently act as barrier to diversification and promote specializing
(Hilborn et al. 2003; Kasperski and Holland 2013). While some of these
specialized fishing strategies may be associated with increased revenue
variability, the benefit may be that they are also associated with increased
revenue.-->

TODO: finish this:
External market forces may interact in concert with management regulations to
promote specialization for fishers or other individuals dependent on natural
resources. With increasing environmental variability and extreme events in
a changing climate [@easterling2000], it is particularly important that
individuals who rely on natural resources as a primary source of income have
strategies to reduce risk. Although variability in individual revenue may not be
actively incorporated into many management decisions, analyses like ours help to
understand the range of diversification strategies available and how their
benefits may change over time.

<!--take home is the management context is key and controls show that
it's more complicated-->

@@

<!-- TODO: get fig:re in results -->
<!-- Our model estimates overall average effects (Fig. S\ref{fig:fe}) and
effects --> <!-- that vary by strategy (Fig. S\ref{fig:re}). -->

>>>>

With increasing environmental variability and extreme events in a changing
climate [@easterling2000], it is particularly important that individuals who
rely on natural resources as a primary source of income, such as fishers,
farmers, and forestry workers, have effective strategies to reduce risk. While
diversification can provide a powerful form of risk buffering, we have shown
that the relationship between individual changes to diversification and income
variability is complex and context specific. Furthermore, external market forces
can interact with management regulations, which have other considerable
benefits, to restrict individual diversification opportunities and promote
specialization. Although variability in individual revenue may not be actively
incorporated into management decisions, analyses such as ours help to understand
the range of diversification strategies available, trade-offs inherent in such
management decisions, and how these trade-offs may change over time.

@@
